Demes: a standard format for demographic models

### 2022-08-08 software-table.tex

>>>>

\MSMC & A script provided in the MSMC-tools repository \url{https://github.com/stschiff/msmc-tools}
    converts MSMC \citep{SchiffelsDurbin2014,WangSchiffels2020} output to the demes format. Instructions are available in the Guide \url{https://github.com/stschiff/msmc-tools/blob/master/msmc-tutorial/guide.md}.\\
